A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-24 doc/Paper1/ms.tex
Wording

\section{GP Covariance Function}
Recall that the noise-free light curves of the two images are given by:
\begin{eqnarray}
y_1(t) &=& m_1 + q(t - \tau_1) + \mu_1(t) \\
y_2(t) &=& m_2 + q(t - \tau_2) + \mu_2(t)
\end{eqnarray}
where $\tau_1 = 0$.
Using this, and the model assumptions discussed above, we can obtain the
covariance of $y_1$ with itself at a different time, as well as $y_2$ with itself
at a different time, and $y_1$ and $y_2$ at any time lag. For distinct images
$i$ and $j$ the covariance is:
\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_j(t_2) - m_j\right)\right]\\
&=& \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_j) + \mu_j(t_2)\right)\right]\\
&=& \mathds{E}\left[q(t_1 - \tau_i)q(t_2 - \tau_j) + q(t_1 - \tau_i)\mu_j(t_2)
+ \mu_i(t_1)q(t_2 - \tau_j) + \mu_i(t_1)\mu_j(t_2)
\right]\\
&=& S_q\exp
\left[-\frac{|(t_2 -\tau_j)- (t_1-\tau_i)|}{L_q}\right].
\end{eqnarray}
For a single image $i$, the covariance is:
\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_i(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_i(t_2) - m_i\right)\right]\\
&=& \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_i) + \mu_i(t_2)\right)\right]\\
&=& \mathds{E}\left[q(t_1 - \tau_i)q(t_2 - \tau_i) + q(t_1 - \tau_i)\mu_i(t_2)
+ \mu_i(t_1)q(t_2 - \tau_i) + \mu_i(t_1)\mu_i(t_2)
\right]\\
&=& S_q\exp
\left[-\frac{|(t_2 -\tau_j)- (t_1-\tau_i)|}{L_q}\right] +
S_i\exp\left[
-\left(\frac{|t_2 - t_1|
}{\ell_i}\right)^\alpha
\right]
.
\end{eqnarray}
The covariance between a data point $Y_i$ and another data point $Y_j$ is
given by the covariance of the underlying noise-free light curves at times $t_i$
and $t_j$, plus a noise term:
\begin{eqnarray}
\textnormal{Cov}\left(
Y_i, Y_j
\right) = \textnormal{Cov}\left(y_{k_i}(t_i), y_{k_j}(t_j)\right)
+ \delta_{ij}\left[\left[\kappa_1 + (\kappa_2 - \kappa_1)\mathds{1}(B_i = 1)\right]\sigma_i\right]^2
\end{eqnarray}
where $\sigma_i$ is the reported error bar given with the data. The coefficient
in front of $\sigma_i$ implies that the error bar should be multiplied by
$\kappa_1$ if this is a ``good'' data point, or by $\kappa_2$ if it is a ``bad''
data point.

>>>>

\section{GP Covariance Function}
Recall that the noise-free light curves of the two images are given by:
\begin{eqnarray}
y_1(t) &=& m_1 + q(t - \tau_1) + \mu_1(t) \\
y_2(t) &=& m_2 + q(t - \tau_2) + \mu_2(t)
\end{eqnarray}
where $\tau_1 = 0$.
Using this, and the model assumptions discussed in the paper, we can obtain the
covariance of image $i$ at time $t_1$ with image $j$ at time $t_2$, where
$i \neq j$:
\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_j(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_j(t_2) - m_j\right)\right]\\
&=& \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_j) + \mu_j(t_2)\right)\right]\\
&=& \mathds{E}\left[q(t_1 - \tau_i)q(t_2 - \tau_j) + q(t_1 - \tau_i)\mu_j(t_2)
+ \mu_i(t_1)q(t_2 - \tau_j) + \mu_i(t_1)\mu_j(t_2)
\right]\\
&=& S_q\exp
\left[-\frac{|(t_2 -\tau_j)- (t_1-\tau_i)|}{L_q}\right].
\end{eqnarray}
We can also obtain the covariance of image $i$ measured at two times $t_1$ and
$t_2$:
\begin{eqnarray}
\textnormal{Cov}\left[y_i(t_1), y_i(t_2)\right]
&=& \mathds{E}\left[\left(y_i(t_1) - m_i\right)\left(y_i(t_2) - m_i\right)\right]\\
&=& \mathds{E}\left[\left(q(t_1 - \tau_i) + \mu_i(t_1)\right)
\left(q(t_2 - \tau_i) + \mu_i(t_2)\right)\right]\\
&=& \mathds{E}\left[q(t_1 - \tau_i)q(t_2 - \tau_i) + q(t_1 - \tau_i)\mu_i(t_2)
+ \mu_i(t_1)q(t_2 - \tau_i) + \mu_i(t_1)\mu_i(t_2)
\right]\\
&=& S_q\exp
\left[-\frac{|(t_2 -\tau_j)- (t_1-\tau_i)|}{L_q}\right] +
S_i\exp\left[
-\left(\frac{|t_2 - t_1|
}{\ell_i}\right)^\alpha
\right]
.
\end{eqnarray}
The covariance between a data point $Y_i$ and another data point $Y_j$ is
given by the covariance of the underlying noise-free light curves at times $t_i$
and $t_j$, plus a noise term:
\begin{eqnarray}
\textnormal{Cov}\left(
Y_i, Y_j
\right) = \textnormal{Cov}\left(y_{k_i}(t_i), y_{k_j}(t_j)\right)
+ \delta_{ij}\left[\left[\kappa_1 + (\kappa_2 - \kappa_1)\mathds{1}(B_i = 1)\right]\sigma_i\right]^2
\end{eqnarray}
where $\sigma_i$ is the reported error bar given with the data. The coefficient
in front of $\sigma_i$ implies that the error bar should be multiplied by
$\kappa_1$ if this is a ``good'' data point, or by $\kappa_2$ if it is a ``bad''
data point.
